Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-03-22 manuscript.tex
Remove redlined.md first [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/6d0a6402c44cb9745875171d2d33c37b4d7fe4be.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/6d0a6402c44cb9745875171d2d33c37b4d7fe4be/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/675578778

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...3c704477904acd1717b7d523cd8714280a4e457e}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/3c704477904acd1717b7d523cd8714280a4e457e/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/3c704477904acd1717b7d523cd8714280a4e457e}{habi/zmk-tooth-cohort-method-manuscript@3c70447}
on March 10, 2021.

@@

Two tooth datasets are available to download in the GitHub repository with the analysis notebook {[}\protect\hyperlink{ref-tZRGGuMm}{22}{]}.
The other datasets used for the current study are available from the corresponding author on reasonable request.

@@

\leavevmode\hypertarget{ref-ydSnvH5h}{}%
28. Anatomical plane - Wikipedia. 2020. \url{https://w.wiki/_K2r}.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. Fedlex. \url{https://www.fedlex.admin.ch/eli/cc/2013/617/en}. Accessed 10 Mar 2021.
\end{cslreferences}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...6d0a6402c44cb9745875171d2d33c37b4d7fe4be}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/6d0a6402c44cb9745875171d2d33c37b4d7fe4be/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/6d0a6402c44cb9745875171d2d33c37b4d7fe4be}{habi/zmk-tooth-cohort-method-manuscript@6d0a640}
on March 22, 2021.

@@

Two tooth datasets are available to download in the GitHub repository with the analysis notebook: https://github.com/habi/zmk-tooth-cohort {[}\protect\hyperlink{ref-tZRGGuMm}{22}{]}.
The other datasets used for the current study are available from the corresponding author on reasonable request.

@@

\leavevmode\hypertarget{ref-ydSnvH5h}{}%
28. \url{https://w.wiki/_K2r}.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. Fedlex. \url{https://www.fedlex.admin.ch/eli/cc/2013/617/en}. Accessed 22 Mar 2021.
\end{cslreferences}
